Racial and Ethnic Differences in ETI: Outcomes

### 2024-07-22 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
uncommented models section

<!-- # LOESS-smoothed outcome plots -->

<!-- ```{r functions} -->
<!-- # Plots -->
<!-- loess_plot <- function(data = encounter, outcome, facet = F) { -->
<!--   p <- ggplot(data, aes(x = Days, y = !!sym(outcome), color = Race)) + -->
<!--     geom_point( -->
<!--       shape = ".", aes(x = Days, y = !!sym(outcome)), inherit.aes = F, -->
<!--       alpha = 0.1 -->
<!--     ) + -->
<!--     geom_smooth(method = "loess", se = F) + -->
<!--     theme_classic() -->
<!--   if (facet) { -->
<!--     p <- p + facet_wrap(~Race) -->
<!--   } -->
<!--   return(p) -->
<!-- } -->
<!-- ``` -->

<!-- ```{r results='asis'} -->
<!-- #| warning: false -->
<!-- invisible(lapply(continuous_outcomes, function(o) { -->
<!--   cat("\n") -->
<!--   cat("\n") -->
<!--   cat("##", o) -->
<!--   cat("\n") -->
<!--   cat("\n") -->
<!--   print(loess_plot(outcome = o)) -->
<!-- })) -->
<!-- ``` -->

>>>>

# LOESS-smoothed outcome plots

```{r functions}
# Plots
loess_plot <- function(data = encounter, outcome, facet = F) {
  p <- ggplot(data, aes(x = Days, y = !!sym(outcome), color = Race)) +
    geom_point(
      shape = ".", aes(x = Days, y = !!sym(outcome)), inherit.aes = F,
      alpha = 0.1
    ) +
    geom_smooth(method = "loess", se = F) +
    theme_classic()
  if (facet) {
    p <- p + facet_wrap(~Race)
  }
  return(p)
}
```

```{r results='asis'}
#| warning: false
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o))
}))
```
